### 2023-10-25 journal/correctness.tex
redid formatting of main algorithm

%\Eric{I think this case was missing from the proof in the thesis}
Now suppose $R$'s call to \op{CreateBlock} returns \nl, causing $R$ to terminate at line \ref{addOP}.
Intuitively, since there are no operations in $\var{v}$'s children to promote, $op$ is already in $\var{v}$.
We formalize this intuition.
The value computed at line \ref{createSumEnq} is
\begin{eqnarray*}
\var{num\sub{enq}} \hspace*{-2mm}
&=& \hspace*{-2mm} \var{v}.\fld{left.blocks}[new.\eleft].\fld{sum\sub{enq}} \\
&& + \var{v}.\fld{right.blocks}[new.\eright].\fld{sum\sub{enq}}\\
&&  - \var{v}.\fld{blocks}[h-1].\fld{sum\sub{enq}} \\
&=& \hspace*{-2mm}\var{v}.\fld{left.blocks}[new.\eleft].\fld{sum\sub{enq}}\\
&& + \var{v}.\fld{right.blocks}[new.\eright].\fld{sum\sub{enq}} \\
&&- \var{v}.\fld{left.blocks}[\var{v}.\fld{blocks}[h-1].\eleft].\fld{sum\sub{enq}} \\
&& - \var{v}.\fld{right.blocks}[\var{v}.\fld{blocks}[h-1].\eright].\fld{sum\sub{enq}}.
\end{eqnarray*}
It follows from \Cref{lem::sum} that $num\sub{enq}$ is the total  number of enqueues  in 
$\var{v}.\fld{left.blocks}[\var{v}.\fld{blocks}[h-1].\eleft+1..new.\eleft]$ and
$\var{v}.\fld{right.blocks}[\var{v}.\fld{blocks}[h-1].\eright+1..new.\eright]$.
Similarly, $num\sub{deq}$ is the total number of dequeues contained in these blocks.
Since $num\sub{enq}+num\sub{deq}=0$ at line \ref{testEmpty},
these blocks contain no operations.
By \Cref{blockNotEmpty}, this means the ranges of blocks are empty, so that $\var{v}.\fld{blocks}[h-1].\eleft \geq \var{new}.\eleft \geq i$.
Hence, $B$ is already a subblock of some block in $\var{v}$, so $\var{v}$ contains $op$.
\end{proof}

>>>>

%\Eric{I think this case was missing from the proof in the thesis}
Now suppose $R$'s call to \op{CreateBlock} returns \nl, causing $R$ to terminate at line \ref{addOP}.
Intuitively, since there are no operations in $\var{v}$'s children to promote, $op$ is already in $\var{v}$.
We formalize this intuition.
The value computed at line \ref{createSumEnq} is
\begin{eqnarray*}
\var{num\sub{enq}}
&=&  \var{v}.\fld{left.blocks}[new.\eleft].\fld{sum\sub{enq}} \\
&& + \var{v}.\fld{right.blocks}[new.\eright].\fld{sum\sub{enq}}\\
&&  - \var{v}.\fld{blocks}[h-1].\fld{sum\sub{enq}} \\
&=& \var{v}.\fld{left.blocks}[new.\eleft].\fld{sum\sub{enq}}\\
&& + \var{v}.\fld{right.blocks}[new.\eright].\fld{sum\sub{enq}} \\
&&- \var{v}.\fld{left.blocks}[\var{v}.\fld{blocks}[h-1].\eleft].\fld{sum\sub{enq}} \\
&& - \var{v}.\fld{right.blocks}[\var{v}.\fld{blocks}[h-1].\eright].\fld{sum\sub{enq}}.
\end{eqnarray*}
It follows from \Cref{lem::sum} that $num\sub{enq}$ is the total  number of enqueues  in 
$\var{v}.\fld{left.blocks}[\var{v}.\fld{blocks}[h-1].\eleft+1..new.\eleft]$ and
$\var{v}.\fld{right.blocks}[\var{v}.\fld{blocks}[h-1].\eright+1..new.\eright]$.
Similarly, $num\sub{deq}$ is the total number of dequeues contained in these blocks.
Since $num\sub{enq}+num\sub{deq}=0$ at line \ref{testEmpty},
these blocks contain no operations.
By \Cref{blockNotEmpty}, this means the ranges of blocks are empty, so that $\var{v}.\fld{blocks}[h-1].\eleft \geq \var{new}.\eleft \geq i$.
Hence, $B$ is already a subblock of some block in $\var{v}$, so $\var{v}$ contains $op$.
\end{proof}
